Dysregulation of Cerebral Hemoglobin Content in Malawian Children with Malaria

### 2021-05-13 figures.Rmd
file rearrange, models 3 & 4

final_rs_res %>% 
  conf_mat_resampled() %>%

  # plot
  ggplot(aes(x = Truth, y = Prediction, fill = Freq, label = Freq)) +
  geom_tile() +
  geom_text(size = 8) +
  scale_fill_gradient2(low = "#4575b4", high = "#d73027") +

@@

glm_res2 %>% 
  conf_mat_resampled() %>% 
  mutate(Prediction = ifelse(Prediction == 1, "CM", "UM")) %>% 
  mutate(Truth = ifelse(Truth == 1, "CM", "UM")) %>%

  # plot
  ggplot(aes(x = Truth, y = Prediction, fill = Freq, label = Freq)) +
  geom_tile() +
  geom_text(size = 6) +
  scale_fill_gradient2(low = "#4575b4", high = "#d73027") +

>>>>

final_res_conf_mat <- final_rs_res %>% conf_mat_resampled() 
final_res_conf_mat %>% 
  group_by(Truth) %>% 
  summarise(total_true = sum(Freq)) %>% 
  right_join(final_res_conf_mat) %>% 
  mutate(`Percent occurence` = round(Freq/total_true*100, 2)) %>%

  # plot
  ggplot(aes(x = Truth, y = Prediction, fill = `Percent occurence`, label = `Percent occurence`)) +
  geom_tile() +
  geom_text(size = 8) +
  scale_fill_gradient2(low = "#4575b4", high = "#d73027") +

@@

final_res_conf_mat2 <- glm_res2 %>% 
  conf_mat_resampled() %>% 
  mutate(Prediction = ifelse(Prediction == 1, "CM", "UM")) %>% 
  mutate(Truth = ifelse(Truth == 1, "CM", "UM"))

final_res_conf_mat2 %>% 
  group_by(Truth) %>% 
  summarise(total_true = sum(Freq)) %>% 
  right_join(final_res_conf_mat2) %>% 
  mutate(`Percent occurence` = round(Freq/total_true*100, 2)) %>%

  # plot
  ggplot(aes(x = Truth, y = Prediction, fill = `Percent occurence`, label = `Percent occurence`)) +
  geom_tile() +
  geom_text(size = 6) +
  scale_fill_gradient2(low = "#4575b4", high = "#d73027") +
